Research Spike: Evaluation of Using a Single Mnemonic both for Cryptocurrency and Identity Wallets

### 2022-01-17 prism-backend/research/single-mnemonic/iowal.tex
Added comments on cryptographic choices by Atala and Cardano.

>>>>

\paragraph{Note on the different cryptographic choices.} As stated, Cardano's
Lightwallet CIP1852 follows a variation of BIP44 where the chosen singing
algorithm is EdDSA, which uses Ed25519 as elliptic curve; whereas Atala builds
from BIP32, thus employs ECDSA with a secp256k1 curve. The reason behind this
difference seems just circumstancial, and due to the fact that Atala started to
build from a different specification. From a cryptographic point of view, it is
possible to unify under the same curve, or to stick to different ones. In the
latter case, however, we must make sure that domain separation is correctly
done: i.e., even if having a sort of unified wallet derived from the same
mnemonic, it should not be possible to generate the same key to be used for
payment purposes and identity purposes. More detail on this is given in
\secref{ssec:unification}.

Other than the previous, either choice seems to have its pros and cons. On the
one hand, having both Cardano and Atala use the same curve would make it
possible to benefit from joint development efforts. Also, it would avoid
pitfalls such as using the same key in different curves, which can lead to
security issues as described next (however, this can also be avoided with proper
domain separation). Also, Edwards curves (such as Ed25519) are, at least in
theory, more efficient. On the other hand, Secp256k1 is an standardized curve,
which has seen more implementation and optimization effort. This means that the
better theoretical efficiency of Ed25519 may somehow ``mitigated'' by more
efficient implementations in Secp256k1. Also, Secp256k1 probably has more
availability of implementations in different programming languages. In any case,
this is something that needs to be considered by the development/engineering
teams.
